Exploring the composition of lithic assemblages in Mesolithic south-eastern Norway

### 2021-07-06 analysis/paper/paper.Rmd
Minor edits

sn <- sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              NodeID = "name", Value = "value",
              sinksRight=TRUE, nodeWidth = 0, fontSize = 10)

>>>>

sn <- sankeyNetwork(Links = links, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              NodeID = "name", Value = "value",
              sinksRight=TRUE, nodeWidth = 0, fontSize = 14)
